Models of lens candidates from Space Warps CFHTLS

### 2017-03-22 parts/stelmass.tex
dbg

In addition, we also derive halo masses for the lenses by use of the
standard abundance matching technique, whereby a comparison of the
observed stellar mass function of galaxies with the dark matter halo
mass function from N-body simulations results in a simple relation
between the two. We emphasize that this derivation of halo mass should
be considered an ``average'' estimate, and a significant scatter can
be expected as galaxies with the same stellar mass can be found in
different environments. We refer the reader to \cite{2012MNRAS.424..104L}
for an assessment of the effect of abundance matching on the
derivation of dark matter halo properties in lensing galaxies. We
follow the prescription of \citet{2010ApJ...710..903M}, namely:
\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/\Mone)^{-\beta} +
                                     (\Mhalo/\Mone)^\gamma} \\
C_0 &= 0.02820, \quad \Mone = 10^{11.884} \Msun \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
and define a halo-matching index:
\begin{equation}
\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
  lensing mass.
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}
This is the last of our model diagnostics, expressing whether the
lensing mass is plausible given the light from the candidate lensing
galaxy.

>>>>

In addition, we also derive halo masses for the lenses by use of the
standard abundance matching technique, whereby a comparison of the
observed stellar mass function of galaxies with the dark matter halo
mass function from $N$-body simulations results in a simple relation
between the two. We emphasize that this derivation of halo mass should
be considered an ``average'' estimate, and a significant scatter can
be expected as galaxies with the same stellar mass can be found in
different environments. We refer the reader to \cite{2012MNRAS.424..104L}
for an assessment of the effect of abundance matching on the
derivation of dark matter halo properties in lensing galaxies. We
follow the prescription of \citet{2010ApJ...710..903M}, namely:
\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/\Mone)^{-\beta} +
                                     (\Mhalo/\Mone)^\gamma} \\
C_0 &= 0.02820, \quad \Mone = 10^{11.884} \Msun \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
%Figure~\ref{fig:stelmass} may be compared with Figure~4 in
%\cite{2011ApJ...734...69M}.

The comparison of lensing and stellar masses provides us with the last
of our model diagnostics.  This is a halo-matching index:
\begin{equation}
\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
  lensing mass.
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}
The halo-matching index expresses whether the lensing mass is
plausible given the light from the candidate lensing galaxy.
